Production-maintenance scheduling in complex machinery

### 2024-03-14 Paper.tex
Expand algo description, benchmark sec, fix ksenia remarks, add couple refs

@@

\subsubsection{Production-maintenance scheduling} ?????? EXPAND ON THE BACKGROUND ????? This problem belongs to the class of production-maintenance scheduling problems with parallel machines - see Geurtsen et al.~\cite{Production_maintenance_and_resource_scheduling_A_review} for a comprehensive literature review. Many variants of this problem exist and have been studied for decades, albeit less than other more classical problems. While some authors opt to model machine failure with a random distribution~\cite{A_decomposition_method_by_interaction_prediction_for_the_optimization_of_maintenance_scheduling, Multi-component_Maintenance_Optimization:_A_Stochastic_Programming_Approach}, the majority of the literature looks at linear variants of this problem (see~\cite{Scheduling_jobs_with_time_resource_tradeoff_via_nonlinear_programming} for a resource-production exception), mostly because physical considerations tend to be ignored in more abstract models.

Recently, approaches using decomposition for maintenance scheduling have appeared in the literature. While some use Bender's decomposition for .... (see cite cite), others use Dantzig-Wolfe decomposition, in a manner similar to ours. Insert name of guy here explored the possibility of using blablabla in his PhD thesis cite.

@@

    Industrial maintenance tends to rely on two heuristics for maintenance scheduling: Time-based Maintenance (TbM), where maintenance is planned considering the time since the last maintenance action, and Condition Based Maintenance (CbM), where the asset is regularly tested and when some predefined threshold is reached, maintenance is scheduled (\hspace{1sp}\cite{cigre445} elaborates on this in the context of power transformers).

    Research on methods for employing just-in-time maintenance is plentiful, with many of these methods resorting to machine learning, with the use of real-world data~\cite{Artificial_Intelligence_Application_for_Just_in_Time_Maintenance}. The idea is to perform maintenance at the precise point in time when any delay in the maintenance action would result in the failure of a component. As will be shown in Example~\ref{ex:non_optimal_JIT_maintenance}, this can lead to suboptimal solutions.

    To make things worse, these strategies are employed independently of the production decisions, thus further straying away from optimality, which highlights the importance of better maintenance practices. \\

@@

\begin{tabular}{ |p{1.25cm}||p{6.5cm}|p{2.5cm}|  }
     \hline
     Variable & Variable Meaning & Variable Type\\
     \hline
     \hline
    $x^k_{n,t}$   &  Maintenance of component $k$ of machine $n$ at period $t$   & Binary\\
    $y_{n,t}$   &  Production of machine $n$ period $t$ & Continuous\\
    $r^k_{n,t}$   &  Condition of component $k$ of machine $n$ at period $t$  & Continuous\\
    \hline
    \end{tabular}
}
        \caption{Description of the variables used in the model}
        \label{tab:abstract_variable_description}    
\end{table}

Below we present a general formulation for the models we will be working with. The variables are represented by lowercase letters ($x,y,r$), parameters by uppercase letters with a different font (\cmss{C}, \cmss{Q}, \cmss{M}, etc.), and sets by uppercase letters with a third font ($\mathcal{N}, \mathcal{K}, \mathcal{Z}$). The subscript $n$ indicates machine $n$, $t$ the time period $t$, and the superscript $k$, component $k$. So $r_{n,t}^k$ is the variable $r$ for component $k$ of machine $n$ at the time period $t$.

\begin{mini!}|l|[3]
    {x,y}{\sum_{n \in \mathcal{N}}\sum_{t \in \mathcal{T}}\sum_{k \in \mathcal{K}^n} C^k \cdot x^k_{n,t}}
{\label{con:cost_minimization_objective}}{}
\addConstraint{\sum_{n \in \mathcal{N}} y_{n,t} \geq \cmss{E}_t \quad &\forall t \in \mathcal{T} \, \forall n \in \mathcal{N}}{\label{con:satisfy_demand}}
\addConstraint{r_{n,t}^k \leq f_{n,k}(r_{n,t-1}^k, y_{n,t}; r_{n,t-1}^1, \dots, r_{n,t-1}^{|\mathcal{K}_n|}) + \cmss{M}\cdot x_{n,t}^k &\forall t,n,k}{\label{con:component_degradation}}
\addConstraint{y_t \leq g_{n,k}(r_{n,t}^k) & \forall t \, \forall n \in \mathcal{N} \, \forall k \in \mathcal{K}}{\label{con:production_limit}}
\addConstraint{y_{n,t} \leq (1-x^k_{n,t})\cdot \cmss{Q}^k \, & \forall t \, \forall n \in \mathcal{N} \, \forall k \in \mathcal{K}}{\label{con:maintenance_downtime}}
\addConstraint{x^k_{n,i} \geq x^k_{n,t} - x^k_{n,t-1}\, & \forall n, k, t \leq i \leq t + \cmss{D}^k}{\label{con:maintenance_duration}}
\addConstraint{x_{n,t}^k \leq x_{n,t}^{k^\prime} \, &\forall t \in \mathcal{T} \, \forall (k, k^\prime) \in \mathcal{Z}}{\label{con:maintenance_implications}}
\addConstraint{x^k_{n,t} \in \{0,1\}}{}
\addConstraint{y_{n,t} \geq 0}{}
\addConstraint{0 \leq r^k_{n,t} \leq \cmss{R}^k_n}{}
\label{model:abstract_formulation}
\end{mini!}

@@

The objective of the model is to minimize the maintenance cost (added over all components of all machines in all time periods) while guaranteeing that the machines satisfy the demand in Constraints~\ref{con:satisfy_demand}. Constraints~\ref{con:component_degradation} model the evolution of the condition of the components. A big-M term represents the maintenance action which, in conjunction with the binary variable $x_{n,t}^k$ will simulate the replacement of the component. Function $f$ will model the (possibly nonlinear) degradation of the component, which depends on its previous condition, the current production, and possibly the condition of the other components of the same machine. Constraints~\ref{con:production_limit} enforce a (possibly nonlinear) upper bound on the production of a machine, based on the condition of its components. A machine with damaged components will not be able to produce as much as a new one. Constraints~\ref{con:maintenance_downtime} stipulate that the machines stop production while one of their components is being maintained, and Constraints~\ref{con:maintenance_duration} impose a predetermined duration for replacing the components. Finally, Constraints~\ref{con:maintenance_implications} represent the interactions between components regarding maintenance, where the replacement of some components forces the maintenance of others.

The following is a valid cut:

\begin{equation*}
x_{n,t}^k \leq x_{n,|\mathcal{T}|-\cmss{D}^k}^k, \quad \forall k, t \geq |\mathcal{T}| - \cmss{D}^k  
\end{equation*}

Since a maintenance action cannot be started if it does not have enough time to be finished.

\section{Dantzig-Wolfe Reformulation}
\label{sec:DW}
    The formulation above exhibits a block diagonal structure with a set of complicating constraints. These are Constraints~\ref{con:satisfy_demand}, requiring that the demand must be satisfied, while the blocks are composed by the functioning of the independent machines. Dantzig-Wolfe decomposition is a method for solving problems with these attributes~\cite{Decomposition_Principle_for_Linear_Programs}. The nonlinearities in the formulation will appear in the pricing problem, thus not directly interfering with the algorithm. Another work with a nonlinear pricing problem can be found in~\cite{Exact_Methods_for_Recursive_Circle_Packing}.

    In the master problem below, we aggregate subproblems if they correspond to identical machines, as they share the same set of possible solutions. With this aggregation, we expect that the usefulness of the reformulation will increase with the number of identical machines, given its symmetry-breaking characteristics. Thus, the value of $\lambda_{z,i}$ will tell us how many machines in the subgroup of identical machines $z$ will use solution $i$. The notation $\cmss{y}_{z,i,t}$ refers to the production of solution $i$ (from the subgroup $z$) at time $t$, and $\cmss{y}$ uses a different font to emphasize that in the master model it is a parameter.

\begin{mini!}|l|[3]
{\lambda}{\sum_{z \in \mathcal{Z}}\sum_{i \in \mathcal{X}_z} c^\intercal \lambda_{z,i}}
{}{}
\addConstraint{\sum_{z \in \mathcal{Z}}\sum_{i \in \mathcal{X}_z} \lambda_{z,i} \cdot \cmss{y}_{z,i,t} \geq \cmss{E}_{t}, \quad & \forall t \in \mathcal{T} &\quad (\pi)}{\label{con:lambda_production_demand}}
\addConstraint{\sum_{i \in \mathcal{X}_z} \lambda_{z,i} = |\mathcal{Z}_z|, & \forall z \in \mathcal{Z} &\quad (\pi_0)}{\label{con:lambda_satisfaction}}
\addConstraint{0 \leq \lambda_{z,i} \leq |\mathcal{Z}_z|, & \forall z \in \mathcal{Z}}
\end{mini!}

Constraints~\ref{con:lambda_production_demand} stipulate that the chosen solutions must satisfy the production demand. Computationally speaking, it makes more sense to use an inequality rather than an inequality, as it tends to allow for a faster stabilization of the corresponding dual values. Constraints~\ref{con:lambda_satisfaction} enforce that each subgroup of identical machines can have at most \textit{size of the subgroup} solutions.

This reformulation is solved with column generation, which will provide new patterns for each of the different sets of machines, looking for the ones with the lowest reduced cost. The dual variables from constraints~\ref{con:lambda_production_demand} will incentivize solutions with a higher production, while the maintenance cost will prevent solutions with too many maintenance actions. The generation of new patterns is obtained by the pricing problem below.

\begin{mini!}|l|[3]
{x,y}{C^\intercal x - \pi^\intercal y - \pi_0}
{}{}
\addConstraint{\text{Constraints~\ref{con:component_degradation}-~\ref{con:maintenance_implications} being satisfied}}{\label{con:machine_operation}}
\addConstraint{y_t \leq \cmss{E}_t\, \forall t \in \mathcal{T}}{\label{con:demand_upper_bound}}
\end{mini!}

Given that the production is a variable in this subproblem, $y$ uses the variable font.

As the production demand is a clear upper bound on the production of any specific machine, Constraint~\ref{con:demand_upper_bound} is a valid cut.

 The pricing problem can also be interpreted in the context of machine production. The objective function is equivalent to the maximization of the profit of a machine (where the selling price of the product at time $t$ is given by the corresponding dual value). The added valid inequality enforces a cap on production, after which the product can not be sold, simulating markets where there is limited demand.
 An application of this problem to power transformers was introduced by Dionísio and Pedroso in~\cite{An_Optimization_Model_for_Power_Transformer_Maintenance}.

@@

\subsubsection{PF} This production-fixing heuristic tries to take advantage of the impact that the production variable has on the model. Given a fixed production vector, the idea is to perform maintenance at the last possible moment, where if any maintenance action were to be delayed by one time period, the solution would be infeasible. This maintenance strategy is called just-in-time maintenance. For a fixed production vector, Constraints~\ref{con:production_limit} will fix the condition of the components, sans the maintenance. Heuristically, the fixed production vector is chosen given the farkas duals or the actual duals of the current iteration. Assuming a normal distribution with mean and standard deviation provided by these duals, the duals that are more unlikely to happen will be benefited. %Heuristically, the decision of which values the variables should be fixed to is being done with pattern-search (also known as the Hooke-Jeeves method)~\cite{Direct_Search_Solution_of_Numerical_and_Statistical_Problems}, where each variable is independently increased and decreased, and improving moves are saved. The algorithm iterates over all the variables until either a time limit or a local optimum is reached.

Even if we pick the best possible production vector, this heuristic is not optimal. This is due to the interaction between the components when it comes to their degradation, but also to the maintenance implication constraints (\ref{con:maintenance_implications}). See the following example.

@@

\begin{algorithm}[h]%[H]
  \SetAlgoLined
  \KwData{$r,y,m$}

  \Do{$\text{\upshape addedMaintenance = TRUE}$}{
    addedMaintenance $\leftarrow$ FALSE\;
    \For{$k^\prime \in \mathcal{K}^n$}{
      \If{$\exists k^{\prime\prime} \mid (k^{\prime\prime}, k^\prime) \in \mathcal{Z} \land x^{k^{\prime\prime}}_t > x^{k^\prime}_t$}{
        addedMaintenance $\leftarrow$ TRUE\;
        \For{$t^\prime \in [t .. t + \cmss{D}^{k^\prime}]$}{
      $y_{t^\prime} \leftarrow 0$\;
      $x^{k^\prime}_{t^\prime} \leftarrow 1$\;
      $r^{k^\prime}_{t^\prime} \leftarrow \cmss{R}^{k^\prime}$\;
      }
    }
    }

@@

??? ALGO DESCRIPTION ALGO DESCRIPTION ALGO DESCRIPTION
Starting with the description of the auxiliary procedure getProduction, 
Now moving onto the main procedure, PF, we start by calling getProduction in line $2$ to obtain the production vector, using the dual values given by the current iteration of the master problem. Setting the

@@

@@

To cope with this, we assume that there are different time periods for production and maintenance decisions. For example, while production decisions are made every hour, maintenance might be planned on a biyearly basis. This forces minor modifications to the formulations, and some more significant ones, as the constraints that combine both $y$ and $x$ variables (like~\ref{con:component_degradation}) need to use the proper indices.

@@

 ??? SLIGHTLY OUTDATED ???

@@

 The instances were randomly generated. They are divided by the number of time periods (either $20$ or $50$), by the number of machines, with some being identical, by the integrality requirements, and they can have ``high'' or ``low'' complexity, meaning that the corresponding machines will have a higher or lower number of components, with more or less interaction between them, respectively. The complexity of the components also affects the degree of nonlinearity in the model.

 It is easy to create instances that favor each of the models, as having more identical machines favors the extended formulation. For this reason, we have opted for creating two sets of instances, with one of them having several identical machines, and the other having fewer.

 We ran both formulations, the compact and the extended models, with a $2h$ time limit.

Each of the results represents the average of $10$ randomly generated instances according to the relevant specification (all with the same complexity, time periods, number of machines). The Time column will show the average time to optimality, for the instances where optimality is achieved, and the Gap (\%) column will show the average Gap for the instances where it was not. The gap is the relative gap: $\frac{|\text{primal bound} - \text{dual bound}|}{ \min(|\text{primal bound}|, |\text{dual bound}|)}$.

The experiments were run on two 6-Core Intel Core i7 with 64 GB running at 3.20GHz. They ran the models with the SCIP solver, version 8.0.0~\cite{scip8.0}. For the implementation, we used its Python interface, PySCIPOpt~\cite{PySCIPOPT}. Some scripts (most importantly visualization with Matplotlib~\cite{matplotlib}) were implemented in Python version 3.7.9.

@@

  On the modeling side, more than one type of maintenance action can make the model more interesting. It increases its difficulty, but it also makes it more realistic, as complete replacement of a component is usually not the only option. The model can also become more general. For example, there might be non-critical components that may be maintained while still allowing for some production of the machine. Another example is the production upper bound in Constraints\ref{con:production_limit}, which might depend not only on the condition of individual components, but also on the joint condition of multiple components.

>>>>

% for having square brackets in constraints
\usepackage{mathtools}

\newtagform{brackets}{[}{]}
\usetagform{brackets}
%

@@

\subsubsection{Production-maintenance scheduling} ?????? EXPAND ON THE BACKGROUND ????? This problem belongs to the class of production-maintenance scheduling problems with parallel machines - see Geurtsen et al.~\cite{Production_maintenance_and_resource_scheduling_A_review} for a comprehensive literature review. Many variants of this problem exist and have been studied for decades, albeit less than other more classical problems. The majority of the literature looks at linear variants of this problem (see~\cite{Scheduling_jobs_with_time_resource_tradeoff_via_nonlinear_programming} for a resource-production exception), mostly because physical considerations tend to be ignored in more abstract models. Other authors avoid the nonlinearities by modeling machine failure with a random distribution~\cite{A_decomposition_method_by_interaction_prediction_for_the_optimization_of_maintenance_scheduling, Multi-component_Maintenance_Optimization:_A_Stochastic_Programming_Approach}, sometimes with Markov chains~\cite{}. In these stochastic models, a few authors perform Bender's decomposition~\cite{Integrated_production_and_maintenance_scheduling_for_a_single_degrading_machine_with_deterioration-based_failures}.

Besides Bender's, some recent works have also used Dantzig-Wolfe decomposition, in a manner similar to ours. Insert name of guy here explored the possibility of using blablabla in his PhD thesis cite.

It is also common to decouple the maintenance and the production decisions, to make the model more tractable~\cite{A_Two-Stage_Framework_for_Power_Transformer_Asset_Maintenance_Management—Part_I:_Models_and_Formulations}. Not performing these decisions at the same time allows the decision horizon for maintenance to be longer, but loses reliability as a result of the assumptions on the production.

@@

    Industrial maintenance tends to rely on two heuristics for maintenance scheduling: Time Based Maintenance (TbM), where maintenance is planned considering the time since the last maintenance action, and Condition Based Maintenance (CbM), where the asset is regularly tested and when some predefined threshold is reached, maintenance is scheduled (\hspace{1sp}\cite{cigre445} elaborates on this in the context of power transformers).

    Research on methods for employing just-in-time maintenance is plentiful, with many of these methods resorting to machine learning, with the use of real-world data~\cite{Artificial_Intelligence_Application_for_Just_in_Time_Maintenance}. The idea is to perform maintenance at the precise point in time when any delay in the maintenance action would result in the failure of a component. As will be shown in Example~\ref{ex:non_optimal_JIT_maintenance} from Section~\ref{sec:heuristics}, this can lead to suboptimal solutions.

    To make things worse, these strategies are employed independently of the production decisions, thus further straying away from optimality, which highlights the importance of better maintenance practices. In the literature, some authors focus on optimizing the maintenance decisions, sometimes modeling degradation probabilistically~\cite{markovian_model_liang_2018}.\\

@@

\begin{tabular}{ |p{1.25cm}||p{6.5cm}|p{2.5cm}|  }
     \hline
     Variable & Variable Meaning & Variable Type\\
     \hline
     \hline
    $x^k_{n,t}$   &  Maintenance of component $k$ of machine $n$ at period $t$   & Binary\\
    $y_{n,t}$   &  Production of machine $n$ at period $t$ & Continuous\\
    $r^k_{n,t}$   &  Condition of component $k$ of machine $n$ at period $t$  & Continuous\\
    \hline
    \end{tabular}
}
        \caption{Description of the variables used in the model}
        \label{tab:abstract_variable_description}    
\end{table}

Below we present a general formulation of the production-maintenance scheduling problem. The variables are represented by lowercase letters ($x,y,r$), parameters by uppercase letters with a different font (\cmss{C}, \cmss{Q}, \cmss{M}, etc.), and sets by uppercase letters with a third font ($\mathcal{N}, \mathcal{K}, \mathcal{Z}$). Varoabçes and parameters will have subscripts and superscripts. For example, $r_{n,t}^k$ is the variable $r$ for component $k$ of machine $n$ at the time period $t$, and this nomenclature is standardized across the model.

\begin{mini!}|l|[3]
    {x,y}{\sum_{n \in \mathcal{N}}\sum_{t \in \mathcal{T}}\sum_{k \in \mathcal{K}^n} C^k \cdot x^k_{n,t}}
{\label{con:cost_minimization_objective}}{}
\addConstraint{\sum_{n \in \mathcal{N}} y_{n,t} \geq \cmss{E}_t \quad &\forall t \in \mathcal{T} \, \forall n \in \mathcal{N}}{\label{con:satisfy_demand}}
\addConstraint{r_{n,t}^k \leq f_{n,k}(r_{n,t-1}^k, y_{n,t}; r_{n,t-1}^1, \dots, r_{n,t-1}^{|\mathcal{K}_n|}) + \cmss{M}\cdot x_{n,t}^k &\forall t,n,k}{\label{con:component_degradation}}
\addConstraint{y_t \leq g_{n,k}(r_{n,t}^k) & \forall t \, \forall n \in \mathcal{N} \, \forall k \in \mathcal{K}}{\label{con:production_limit}}
\addConstraint{y_{n,t} \leq (1-x^k_{n,t})\cdot \cmss{Q}^k \, & \forall t \, \forall n \in \mathcal{N} \, \forall k \in \mathcal{K}}{\label{con:maintenance_downtime}}
\addConstraint{x^k_{n,i} \geq x^k_{n,t} - x^k_{n,t-1}\, & \forall n, k, t \leq i \leq t + \cmss{D}^k}{\label{con:maintenance_duration}}
\addConstraint{x_{n,t}^k \leq x_{n,t}^{k^\prime} \, &\forall t \in \mathcal{T} \, \forall (k, k^\prime) \in \mathcal{Z}}{\label{con:maintenance_implications}}
\addConstraint{x^k_{n,t} \in \{0,1\} \, &\forall t \, \forall n \in \mathcal{N} \, \forall k \in \mathcal{K}}{}
\addConstraint{y_{n,t} \geq 0 \, &\forall t \, \forall n \in \mathcal{N}}{}
\addConstraint{0 \leq r^k_{n,t} \leq \cmss{R}^k_n \, & \forall t \, \forall n \in \mathcal{N} \, \forall k \in \mathcal{K}}{}
\label{model:abstract_formulation}
\end{mini!}

@@

The objective of the model is to minimize the maintenance cost (added over all components of all machines in all time periods) while guaranteeing that the machines satisfy the demand in Constraints~\eqref{con:satisfy_demand}. Constraints~\eqref{con:component_degradation} model the evolution of the condition of the components. A big-M term represents the maintenance action which, in conjunction with the binary variable $x_{n,t}^k$ will simulate the replacement of the component. Function $f$ will model the (possibly nonlinear) degradation of the component, which depends on its previous condition, the current production, and possibly the condition of the other components of the same machine. Constraints~\eqref{con:production_limit} enforce a (possibly nonlinear) upper bound on the production of a machine, based on the condition of its components. A machine with damaged components will not be able to produce as much as a new one. Constraints~\eqref{con:maintenance_downtime} stipulate that the machines stop production while one of their components is being maintained, and Constraints~\eqref{con:maintenance_duration} impose a predetermined duration for replacing the components. Finally, Constraints~\eqref{con:maintenance_implications} represent the interactions between components regarding maintenance, where the replacement of some components forces the maintenance of others.

Since a maintenance action cannot be started if it does not have enough time to be finished, the following is a valid cut: $x_{n,t}^k \leq x_{n,|\mathcal{T}|-\cmss{D}^k}^k, \forall k, t \geq |\mathcal{T}| - \cmss{D}^k$.

\section{Dantzig-Wolfe Reformulation}
\label{sec:DW}
    The formulation above exhibits a block diagonal structure with a set of complicating constraints. These are Constraints~\eqref{con:satisfy_demand}, requiring that the demand must be satisfied, while the blocks are composed of the constraints describing the functioning of the independent machines. Dantzig-Wolfe decomposition is a method for solving problems with these attributes~\cite{Decomposition_Principle_for_Linear_Programs}. The nonlinearities in the formulation will appear in the pricing problem, thus not directly interfering with the algorithm. Other works with nonlinear pricing problems can be found in~\cite{Exact_Methods_for_Recursive_Circle_Packing, Security_Constrained_Economic_Dispatch_Using_Nonlinear_Dantzig-Wolfe_Decomposition} ADD MORE PAPERS HERE.

    In the master problem below, we aggregate subproblems if they correspond to identical machines, as they share the same set of possible solutions. With this aggregation, we expect that the usefulness of the reformulation will increase with the number of identical machines, given its symmetry-breaking characteristics. Thus, the value of $\lambda_{z,i}$ will tell us how many machines in the subgroup $z$ of identical machines will use solution $i$. The notation $\cmss{y}_{z,i,t}$ refers to the production in solution $i$ (from the subgroup $z$) at time $t$, and $\cmss{y}$ uses a different font to emphasize that in the master model it is a parameter.

\begin{mini!}|l|[3]
{\lambda}{\sum_{z \in \mathcal{Z}}\sum_{i \in \mathcal{X}_z} c^\intercal \lambda_{z,i}}
{}{}
\addConstraint{\sum_{z \in \mathcal{Z}}\sum_{i \in \mathcal{X}_z} \lambda_{z,i} \cdot \cmss{y}_{z,i,t} \geq \cmss{E}_{t}, \quad & \forall t \in \mathcal{T} &\quad (\pi)}{\label{con:lambda_production_demand}}
\addConstraint{\sum_{i \in \mathcal{X}_z} \lambda_{z,i} \leq |\mathcal{Z}_z|, & \forall z \in \mathcal{Z} &\quad (\pi_0)}{\label{con:lambda_satisfaction}}
\addConstraint{0 \leq \lambda_{z,i} \leq |\mathcal{Z}_z|, & \forall z \in \mathcal{Z}}
\end{mini!}

Constraints~\eqref{con:lambda_production_demand} stipulate that the chosen solutions must satisfy the production demand. Computationally speaking, it makes more sense to use an inequality rather than an equation, as it tends to allow for a faster stabilization of the corresponding dual values. Constraints~\eqref{con:lambda_satisfaction} enforce that each subgroup of identical machines can have at most \textit{size of the subgroup} solutions.

This reformulation is solved with column generation, which will provide new production-maintenance patterns for each of the different sets of machines, looking for the ones with the lowest reduced cost. The dual variables from constraints~\eqref{con:lambda_production_demand} will incentivize solutions with a higher production, while the maintenance cost will prevent solutions with too many maintenance actions. The generation of new patterns is obtained by the pricing problem below.

\begin{mini!}|l|[3]
{x,y}{C^\intercal x - \pi^\intercal y - \pi_0}
{}{}
\addConstraint{\text{Constraints~\eqref{con:component_degradation}-~\eqref{con:maintenance_implications} being satisfied}}{\label{con:machine_operation}}
\addConstraint{y_t \leq \cmss{E}_t\, \forall t \in \mathcal{T}}{\label{con:demand_upper_bound}}
\end{mini!}

Since the production is a variable in this subproblem, $y$ uses the variable font.

As the production demand is a clear upper bound on the production of any specific machine, Constraint~\eqref{con:demand_upper_bound} is a valid cut.

 The pricing problem can also be interpreted in the context of machine production. The objective function is equivalent to the maximization of the profit of a machine (where the selling price of the product at time $t$ is given by the corresponding dual value). The added valid inequality enforces a cap on production, after which the product can not be sold, simulating markets where there is limited demand.
 A special case of this problem to power transformers was introduced by Dionísio and Pedroso in~\cite{An_Optimization_Model_for_Power_Transformer_Maintenance}.

@@

\subsubsection{PF} This production-fixing heuristic tries to take advantage of the impact that the production variable has on the model. Given a fixed production vector, the idea is to perform maintenance at the last possible moment, where if any maintenance action were to be delayed by one time period, the solution would be infeasible. This maintenance strategy is called just-in-time maintenance. For a fixed production vector, Constraints~\eqref{con:production_limit} will fix the condition of the components, sans the maintenance. Heuristically, the fixed production vector is chosen given the farkas duals or the actual duals of the current iteration. Assuming a normal distribution with mean and standard deviation provided by these duals, the duals that are more unlikely to happen will be benefited. %Heuristically, the decision of which values the variables should be fixed to is being done with pattern-search (also known as the Hooke-Jeeves method)~\cite{Direct_Search_Solution_of_Numerical_and_Statistical_Problems}, where each variable is independently increased and decreased, and improving moves are saved. The algorithm iterates over all the variables until either a time limit or a local optimum is reached.

Even if we pick the best possible production vector, this heuristic is not optimal. This is due to the interaction between the components when it comes to their degradation, but also to the maintenance implication constraints (\eqref{con:maintenance_implications}). See the following example.

@@

\begin{algorithm}[h]%[H]
  \SetAlgoLined
  \KwData{$r,y,x$}

  \Do{$\text{\upshape addedMaintenance = TRUE}$}{
    addedMaintenance $\leftarrow$ FALSE\;
    \For{$k^\prime \in \mathcal{K}^n$}{
      \If{$\exists k^{\prime} \mid (k^\prime, k) \in \mathcal{Z} \land x^{k^{\prime}}_t < x^{k}_t$}{
        addedMaintenance $\leftarrow$ TRUE\;
        \For{$t^\prime \in [t .. t + \cmss{D}^{k^\prime}]$}{
      $y_{t^\prime} \leftarrow 0$\;
      $x^{k^\prime}_{t^\prime} \leftarrow 1$\;
      $r^{k^\prime}_{t^\prime} \leftarrow \cmss{R}^{k^\prime}$\;
      }
    }
    }

@@

Starting with the description of the auxiliary procedure getProduction, we assume that the dual values follow a normal distribution with mean and standard deviation equal to the average and the standard deviation of the dual values, and calculate the cumulative probability of each. Dual values that are unexpectedly high will result in a higher production.

Now moving onto the main procedure, PF, we start by calling getProduction to obtain the production vector, using the dual values given by the current iteration of the master problem. Iterating first over the components and then over the time periods (otherwise the impact that the components have on each others' condition would be incorrect), we compute the condition of the current component for the current time period, as every variable of Constraint~\ref{con:component_degradation} is fixed, sans maintenance. If the resulting condition is incompatible with the production (see Constraint~\ref{con:production_limit}), then maintenance is scheduled. This means setting production to $0$, the condition to its optimal value, and the maintenance variables to $1$, for the duration of component $k$'s maintenance (lines $11-14$).

Due to Constraints~\ref{con:maintenance_implications}, we need to ensure that the maintenance implications are satisfied. We do this in Algorithm~\ref{algo:maintenanceDependencies}. Iterating over all components $k$, if we find a component $k^\prime$ such that $(k^\prime,k) \in \mathcal{Z}$ (and so $x^{k^\prime}_t \leq x^k_t$) which is not maintained, we schedule its maintenance. After doing this, we need to repeat the procedure, as the scheduling of $x^{k^\prime}_t$ might imply the maintenance of other components (if $\exists k^{\prime\prime} \mid (k^{\prime\prime}, k^\prime) \in \mathcal{Z} \land x^{k^{\prime\prime}}_t = 0$). This is done until no more maintenance actions are added.

After scheduling these maintenance actions, we need to recompute the condition of the components that suffered damage from the production in this time period. Since the production was set to $0$ only when analyzing component $k$, the components that preceded it were incorrectly damaged.

@@

This heuristic also assumes the concavity of function $f$, as otherwise ?????. However, it is difficult to describe an example where this would not be the case, in the context of production-maintenance scheduling.

@@

To cope with this, we assume that there are different time periods for production and maintenance decisions. For example, while production decisions are made every hour, maintenance might be planned on a biyearly basis. This forces minor modifications to the formulations, and some more significant ones, as the constraints that combine both $y$ and $x$ variables (like~\eqref{con:component_degradation}) need to use the proper indices.

@@

@@

 The instances were randomly generated. They are divided by the number of time periods (either $10$, $20$, or $50$), by the number of machines, with some being identical, and they can have ``high'' or ``low'' complexity, meaning that the corresponding machines will have a higher or lower number of components, with more or less interaction between them, respectively. The complexity of the components also affects the amount of nonlinearity in the model. For each of these combinations, we generate $10$ different instances.

 It is easy to create instances that favor each of the models, as having more identical machines favors the extended formulation. For this reason, we have opted for creating three sets of instances, with one of them having several identical machines, one other having many dissimilar machines, and an intermediate set.

 For every instance, we ran the three formulations with a $2$h time limit each. The tree formulations are the compact formulation, the extended formulation with exact pricing, and the extended formulation with heuristic pricing.

Each of the results represents the average of the $10$ randomly generated instances according to the relevant specification (all with the same complexity, time periods, number of machines). The Time column will show the average time to optimality, for the instances where optimality is achieved, and the Gap (\%) column will show the average Gap for the instances where it was not. The gap is the relative gap: $\frac{|\text{primal bound} - \text{dual bound}|}{ \min(|\text{primal bound}|, |\text{dual bound}|)}$.

The experiments were run on two 6-Core Intel Core i7 with 64 GB running at 3.20GHz. They ran the models with the SCIP solver, version 9.0.0~\cite{scip9.0}. For the implementation, we used its Python interface, PySCIPOpt~\cite{PySCIPOPT}, version 5.0. Some scripts (most importantly visualization with Matplotlib~\cite{matplotlib}) were implemented in Python version 3.11.4.

@@

  On the modeling side, more than one type of maintenance action can make the model more interesting. It increases its difficulty, but it also makes it more realistic, as complete replacement of a component is usually not the only option. The model can also become more general. For example, there might be non-critical components that may be maintained while still allowing for some production of the machine. Another example is the production upper bound in Constraints\eqref{con:production_limit}, which might depend not only on the condition of individual components, but also on the joint condition of multiple components.
